R for Clinical Study Reports and Submission

### 2021-11-16 tlf-efficacy-km.Rmd
loaded package update

```{r}
library(haven) # Read SAS data
library(dplyr) # Manipulate data
library(tidyr) # Manipulate data
library(r2rtf) # Reporting in RTF format
library(survival) # fit survival model
library(survminer) # plot nice KM plot with risk table
```

>>>>

```{r}
library(haven) # Read SAS data
library(dplyr) # Manipulate data
library(r2rtf) # Reporting in RTF format
library(survival) # fit survival model
library(survminer) # plot nice KM plot with risk table
library(forcats) # Reorder ordinal variable level based on preference 
```
